The Calculus of Linear Constructions

### 2021-10-20 writing/lics22/lics22.tex
lics22

  \begin{figure}[h]
    \vspace{-0.8em}
    \caption{Select Elimination Rules}
    \begin{mathpar}
      \inferrule
      { \Gamma_1 \vdash m : \unit \\ 
        \Gamma_2 \vdash n : A \\
        \mrg{\Gamma_1}{\Gamma_2}{\Gamma} }
      { \Gamma \vdash \letin{()}{m}{n} : A }
      \rname{Unit-Elim}

@@

  \begin{figure}[h]
  \vspace{-1em}
  \caption{Law 1}
  \begin{lstlisting}
  let [ _, c ] := new _ 1 in
  let [ xeq, c ] := get _ _ _ c in
  let [ yeq, c ] := get _ _ _ c in
  let ( x, pf1 ) := xeq in
  let ( y, pf2 ) := yeq in
  let pf1 := Eq_sym _ _ _ pf1 in
  let pf : Eq _ x y := 
    Eq_trans _ _ _ _ pf1 pf2 
  in free _ _ _ c.
  \end{lstlisting}
  \vspace{-1em}
  \label{law1}
  \Description{}
  \end{figure}

@@

  \begin{figure}[h]
  \vspace{-1em}
  \caption{Law 2}
  \begin{lstlisting}
  let [ _, c ] := new _ 1 in
  let c := set _ _ _ _ c 2 in
  let [ zeq, c ] := get _ _ _ c in
  let ( z, pf1 ) := zeq in
  let pf : Eq _ 2 z := pf1 in
  free _ _ _ c.
  \end{lstlisting}
  \vspace{-1em}
  \label{law2}
  \Description{}
  \end{figure}

@@

  \begin{figure}[h]
  \vspace{-1em}
  \caption{Linear Lists}
  \begin{lstlisting}
  Inductive list (A : Type) : Linear :=
  | nil : list A
  | cons : A -> list A -> list A.

  Fixpoint append (A : Type) : list A -o 
    list A -o (list A -o list A) -o list A 
  :=
    fun ls1 ls2 k =>
      match ls1 with
      | nil => k ls2
      | (cons h t) as _cons_ => 
        append _ t ls2 
          (fun res => k (_cons_ h res))
      end.
  \end{lstlisting}
  \label{list}
  \vspace{-1em}
  \Description{}
  \end{figure}

>>>>

  \begin{figure}[h]
    \vspace{-1em}
    \caption{Select Elimination Rules}
    \begin{mathpar}
      \inferrule
      { \Gamma_1 \vdash m : \unit \\ 
        \Gamma_2 \vdash n : A \\
        \mrg{\Gamma_1}{\Gamma_2}{\Gamma} }
      { \Gamma \vdash \letin{()}{m}{n} : A }
      \rname{Unit-Elim}

@@

  \begin{figure}[h]
  \vspace{-0.6em}
  \caption{Law 1}
  \begin{lstlisting}
  let [ _, c ] := new _ 1 in
  let [ xeq, c ] := get _ _ _ c in
  let [ yeq, c ] := get _ _ _ c in
  let ( x, pf1 ) := xeq in
  let ( y, pf2 ) := yeq in
  let pf1 := Eq_sym _ _ _ pf1 in
  let pf : Eq _ x y := 
    Eq_trans _ _ _ _ pf1 pf2 
  in free _ _ _ c.
  \end{lstlisting}
  \vspace{-0.6em}
  \label{law1}
  \Description{}
  \end{figure}

@@

  \begin{figure}[h]
  \vspace{-0.6em}
  \caption{Law 2}
  \begin{lstlisting}
  let [ _, c ] := new _ 1 in
  let c := set _ _ _ _ c 2 in
  let [ zeq, c ] := get _ _ _ c in
  let ( z, pf1 ) := zeq in
  let pf : Eq _ 2 z := pf1 in
  free _ _ _ c.
  \end{lstlisting}
  \vspace{-0.6em}
  \label{law2}
  \Description{}
  \end{figure}

@@

  \begin{figure}[h]
  \vspace{-0.6em}
  \caption{Linear Lists}
  \begin{lstlisting}
  Inductive list (A : U) : L :=
  | nil : list A
  | cons : A -> list A -> list A.

  Fixpoint append (A : U) : list A -o 
    list A -o (list A -o list A) -o list A 
  :=
    fun ls1 ls2 k =>
      match ls1 with
      | nil => k ls2
      | (cons h t) as _cons_ => 
        append _ t ls2 
          (fun res => k (_cons_ h res))
      end.
  \end{lstlisting}
  \label{list}
  \vspace{-0.6em}
  \Description{}
  \end{figure}
